Using Model Checking to Analyze the System Behavior of the LHC Production Grid

### 2013-02-12 ElsevierFGCS_singleColumn.tex
deductive verification added to related work.

>>>>

Static analysis is, in a sense, an extreme form of automated deductive
verification.  In its original form, deductive verification technology
allowed for the use of logics such as Floyd-Hoare logic~\cite{Hoa:69} for
showing the correctness of a software or hardware system by constructing
proofs thereof, based on mathematical descriptions of the behavior of
the system.  These days, the proofs involved are often discharged using a
mechanical or an automated theorem prover. Moreover, more advanced logics
such as Separation Logic~\cite{Rey:02} are used. Deductive verification
is applied quite successfully on software code~\cite{PMSJP:12,KAE+:10}
and hardware~\cite{AATH:10}, but the effort required for conducting the
verification can be prohibiting, and can compare poorly to model checking.
